\thesistitle

### 2019-07-23 sections/clonerefactor.tex
More todo
OKay this is harder than I thought
Common interface
Removing redundant clone classes: conceptual method is enough

\section{JavaParser}
A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}. JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST). JavaParser allows to modify this AST and write the result back to Java source code. This allows us to apply refactorings to the detected problems in the source code.

@@

\subsubsection{Conceptual method of removing redundant clone classes}\label{sec:conceptualremovingredundant}
The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of an existing clone. We define the subset relation between clones as follows:

@@

For CloneRefactor we used this conceptual method of removing duplicates, but did not directly implement these equations. The main reason for this is the runtime overhead, as this process has to iterate over each existing clone class and each of their clone instances. For large projects with a lot of duplication this process has a significant impact on performance.

\subsubsection{CloneRefactor method of removing redundant clone classes}
Because of the order in which clones are found in the clone graph, removing redundant clone classes can be optimized to not require a search of the entire set of clones. To do this, we mark each node that has been considered for duplication as \textit{visited}. This includes nodes that are interated over and all duplicates of those nodes. When we later find a new clone class of which all nodes are \textit{visited}, we don't add this clone class to the set of clone classes because it is a subset of an existing clone class.

\todo{Removal of existing clones: How does this is possibly redundant thing work?}

@@

\subsection{Checking for type 3 opportunities}

>>>>

\section{JavaParser}
A very important design decision for CloneRefactor is the usage of a library named JavaParser \cite{tomassetti2017javaparser}. JavaParser is a Java library which allows to parse Java source files to an abstract syntax tree (AST\footnote{An AST is a tree-representation of a source code file.}). JavaParser allows to modify this AST and write the result back to Java source code. This allows us to apply refactorings to the detected problems in the source code.

@@

\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
The clone detection method used by CloneRefactor can, for various reasons,%Should I list these? Listing them could be a section on its own, as I'd have to show examples to make it concrete.
result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of an existing clone. We define the subset relation between clones as follows:

@@

If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes. This way we avoid redundant clone classes being detected by CloneRefactor.

@@

\subsection{Checking for type 3 opportunities}
\todo{TODO}
